---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/images/"
)
```
```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

# quanteda.textplots: plots and visualisation for quanteda

<!-- badges: start -->
[![CRAN Version](https://www.r-pkg.org/badges/version/quanteda.textplots)](https://CRAN.R-project.org/package=quanteda.textplots)
`r badge_devel("quanteda/quanteda.textplots", "royalblue")`
[![Downloads](https://cranlogs.r-pkg.org/badges/quanteda.textplots)](https://CRAN.R-project.org/package=quanteda.textplots)
[![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/quanteda.textplots?color=orange)](https://CRAN.R-project.org/package=quanteda.textplots)
[![R build status](https://github.com/quanteda/quanteda.textplots/workflows/R-CMD-check/badge.svg)](https://github.com/quanteda/quanteda.textplots/actions)
[![codecov](https://codecov.io/gh/quanteda/quanteda.textplots/branch/master/graph/badge.svg)](https://codecov.io/gh/quanteda/quanteda.textplots) [![DOI](http://joss.theoj.org/papers/10.21105/joss.00774/status.svg)](https://doi.org/10.21105/joss.00774)
<!-- badges: end -->

## About

Contains the `textplot_*()` functions formerly in **quanteda**.  For more details, see https://quanteda.io.

## How to Install

The normal way from CRAN, using your R GUI or 
```{r eval = FALSE}
install.packages("quanteda.textplots") 
```

Or for the latest development version:
```{r eval = FALSE}
# devtools package required to install quanteda from Github 
devtools::install_github("quanteda/quanteda.textplots") 
```

## How to cite

Benoit, Kenneth, Kohei Watanabe, Haiyan Wang, Paul Nulty, Adam Obeng, Stefan Müller, and Akitaka Matsuo.  (2018) "[quanteda: An R package for the quantitative analysis of textual data](https://www.theoj.org/joss-papers/joss.00774/10.21105.joss.00774.pdf)".  _Journal of Open Source Software_.  3(30), 774. [https://doi.org/10.21105/joss.00774](https://doi.org/10.21105/joss.00774).

For a BibTeX entry, use the output from `citation(package = "quanteda.textplots")`.
